\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-09-19 experience.tex
minor edits

The modeling and testing approach described in earlier sections of the paper is not specific to the vNext system. \psharp is a generic framework, capable of handling arbitrary distributed systems. We showcase this capability by presenting developer experience in using \psharp to model and test two other distributed storage systems used in production in Microsoft: the Live Azure Table Migration library; and the Azure Service Fabric system.

>>>>

The modeling and testing approach described in earlier sections of the paper is not specific to the vNext system. \psharp is a generic framework. We showcase this capability by presenting developer experience of using \psharp to model and test two other distributed storage systems used in production in Microsoft.
